\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles\\[1em] Supplementary material

### 2019-06-21 IPANEMAP-2019.tex
Updates from Overleaf

% Enter dates of publication
\copyrightyear{2019}
\pubdate{31 July 2019}
\pubyear{2019}
\jvolume{XX}
\jissue{YY}

@@

\history{%
Received January 1, 2019;
Revised February 1, 2019;
Accepted March 1, 2019}

@@

\subsection*{The \OurTool{} method}
\bsi{Ce chapitre est vraiment très réussi, il explique vraiment bien ce qu'on fait et c'est accessible meme pour des polios de biologistes. je trouve dommage qu'il soit cantoné au Mat et Met. A mon avis il faudrait soit le mettre tel quel comme premier chapitre des résultats, soit en faire une version light sans les détails de calculs le mettre comme premier chapitre des résultats et ne laisser que les calculs dans le Mat et Met}  
\ypi{Dans la mesure où l'intro est courte, et étant donné le titre, je ne pense pas que sa présence en Mat Met limite  sur visibilité. En plus, c'est typiquement là où tu le trouves d'habitude dans ce type de papier (cf Rsample).} \bsi{OK je propose la chose suivante:on laisse tt comme ca le math et met, mais on commence les résultats par un mini-chapitre du genre "principles of IPANEMAP" IPANEMAP relies on .. prediction with RNAsubopt ... sampling ... clustering .. evaluation by front pareto.. Its originality relies on ... See material and methods for details }
We introduce the Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles (\OurTool{}), a novel approach that integrates the signal produced by various chemical probes. It performs clustering based on multiple sets of structures sampled in different experimental conditions, to ultimately return a set of structures that are representative of the dominant clusters. Its underlying rationale is that the prominent presence of a stable secondary structure within the  (pseudo-)Boltzmann ensembles induced by multiple experimental conditions should increase its likelihood to be (one of) the native structure(s) for a given RNA. It is thus hoped that integrating several reactivity profiles may be used to promote the native structure as one of the dominant structures within the multi-ensemble, and help circumvent the limitation of pseudo-energies derived from single reactivity profile, which are generally not sufficient to elect the native structure as its minimum (pseudo)-free energy candidate. In other words, combining ensembles of structures generated using multiple probing experiments is likely to denoise the Boltzmann (multi-)ensemble, and thus mitigate systematic biases induced by experimental conditions and reagents.

@@

Our method, summarized in Figure~\ref{fig:approach}, takes as input a set $\mathcal{D}$ of probing experiments, each materialized by a reactivity profile. It starts by producing sets of representatives structures for each of the reactivity profiles using a SHAPE-directed variant of the classic Ding-Lawrence algorithm~\citep{Ding2003}. Following Deigan\etal\cite{Deigan2009}, soft constraints are used to complement the free energy contributions of the classic Turner energy model with pseudo energy contributions resulting from reactivity profiles derived from SHAPE probing experiments.  Given a reactivity $R_i$ for a position $i$, we associate a free-energy bonus to unpaired positions, defined as
$$\Delta G(i) = m \log(R_i +1 )+b$$ 
using $m=1.3$ and  $b=-0.4$.\bsi{j'avais cru comprendre que ces valeurs avaient été adapté pour IPANEMAP. Sont elles paramétrables lorsuq'ion lance IPANEMAP? Si oui il faudrait peut etre en toucher un mot qque part?} Those values are compared to those used by Deigan\etal\cite{Deigan2009}, based on the rationale that lower absolute values for pseudo-energy bonuses increase the chance of structures being simultaneously supported by multiple conditions. Those pseudo energy contributions effectively direct our predictions towards a subset of structures that are in good agreement with probing data.

@@

\paragraph{Cheng  \emph{et al} dataset.} 
Starting from the assumption that a functional structure should be preserved during evolution, we wanted to assess the agreement that might exist between probing data profiles for a set of RNA mutants. 
We considered DMS probing data, generated by~\cite{Cheng2017} through systematic point-wise mutations, for the Lariat-capping ribozyme. We renormalized each reactivity profile following the method introduced by Deigan\etal\cite{Deigan2009}, restricted to the primer-free sequence: values greater than $1.5 $ times the interquartile range were discarded, and remaining values were divided by the mean of the top $10\%$ reactivities.  Overall, this constitutes a collection of 188 sequences, each having its associated reactivity profile.

@@

\paragraph{Stops-inducing probing protocol (SHAPE-CE).} 
6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature during 10 minutes in the probing buffer (40 mM HEPES at 7.5 pH, 100 mM KCl, in presence or absence of 5 mM MgCl$_\text{2}$. After a 10 minutes incubation at 37\degree{}C, RNAs were treated with 2 mM of SHAPE reagent or DMSO (negative control) and incubated for 2 (BzCN), 5 (1M7), 30 (NMIA) or 60 (NAI) minutes at 37\degree{}C. Modified or unmodified RNAs were purified by ethanol precipitation and pellets were resuspended in 10 $\mu$l of water.
Modifications were revealed by reverse transcription using 5' fluorescently labelled primers (D2 or D4 WellRED, Sigma Aldrich 5' CTG-TGA-ACT-AAT-GCT-GTC-CTT-TAA 3') and M-MLV RNAse (H-) reverse transcriptase (Promega) as previously described~\cite{Deforges2017}, with only minor modification of the originally described SHAPE protocol~\cite{Wilkinson2006}. cDNAs were separated by capillary electrophoresis (Beckman Coulter, Ceq8000). Data were analyzed using the  \Software{QuSHAPE}~\cite{Karabiber2013} software. RNA probing was performed in triplicate with distinct RNA preparations. The corresponding data sets are named after the probe followed by "-CE" and Mg if probed in presence of MgCl$_\text{2}$.

@@

For \OneMSevILUThreeMg, the denaturation step was repeated three times : After a 1 minute incubation at 95\degree{}C, 10 mM of 1M7 was added and the mix was incubated 1 minute at 95\degree{}C. This step was repeated 3 times (3D). For 1M7, 1M7Mg, NMIA and NMIAMg, experiments were conducted as described above, except that the NGS library preparation was adapted to Ion Torrent sequencing. Sequences were mapped and analyzed with \Software{ShapeMapper2} for \OneMSevILUThreeMg and \OneMSevILUThreeMg. For the other conditions they are mapped with a script based on \Software{ShapeMapper}, but adapted to Ion Torrent output files. The corresponding data sets are named after the probe followed by "-MAP", Mg if probed in presence of MgCl$_\text{2}$, and IL  or IT for Illumina or Ion Torrent sequencing, respectively.

\paragraph{DiMethylSulfate (DMS) and CMCT probing.}
DMS and CMCT probing were conducted essentially as described in~\cite{Weill2004,James2008}. Succinctly, 6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature for 10 minutes in a probing buffer for DMS probing (40 mM HEPES pH 7.5, 100 mM KCl, 5 mM MgCl$_\text{2}$) or in CMCT (50 mM of potassium borate pH 8, 100 mM KCl and 5 mM MgCl$_\text{2}$). For DMS, RNA was then treated with 1 $\mu$l of DMS (1:12 in ethanol) or 1 $\mu$l of ethanol for 5 minutes at 37\degree{}C (mock reaction), the reaction was stopped by addition of 400 mM of Tris at 7.5 pH and immediately put on ice. For CMCT,  RNA was treated with 10 $\mu$l of CMCT (42 mg/mL) or 10 $\mu$l H$_\text{2}$O for 10 minutes at 37\degree{}C (mock reaction). Modified RNA were ethanol-precipitated and resuspended in 10 $\mu$l of water. Modifications were mapped as described above for SHAPE-CE experiments.The corresponding data sets are named after the probe followed by "-CE" and Mg.

@@

	\caption{Model of the Lariat capping ribozyme from {\itshape Didymium iridis} (A -- PDB 4P8Z:A by Meyer\etal\cite{Meyer2014}), secondary structure, as annotated by \Software{DSSR} (B -- pseudoknot ommitted) and \OurTool first-ranking prediction (C.), obtained from the integration of 8 maximally-diverging probing conditions (\NMIAMg, \OneMSevILUThreeMg, \NAIMg, \OneMSevCE, \CMCTMg,\OneMSevILUThree, and \OneMSevMgCE).\label{fig:didy}}
\end{figure*}
As benchmark RNA we used the Lariat capping ribozyme from \textit{Didymium Iridis} (DiLCrz) which 3D structure has been modeled at 3,85 A from X-ray diffraction data~\cite{Meyer2014}. This RNA contains a large diversity of interactions, including helical domains, tertiary pairings, a kissing loop and a pseudoknot (Figure~\ref{fig:didy}).
It was probed as described in Material and Methods in 16 different conditions using different SHAPE and classical reagents, in presence/absence of Mg$^\text{2+}$ ions, using either the standard premature stop or the newly developed mutation induction technologies to map the modification sites. These experimental results were then used as input of \OurTool{}, either individually or combined,  for secondary structure prediction.

@@

The average ensemble distance and PCA visualization support a status of outliers for conditions in the cluster \Bull{B} (\OneMSevCE, \NMIACE, \BzCN, and \NAICE).  We hypothesize that such conditions may be either representative of alternative conformations, or be altogether erroneous. Consequently, we will single out these two clusters within our detailed analysis of the multi-probing performances.

\bsi{sauf erreur de ma part le cluster B des parias c'est tous les CE sans Mg .je me demande s'ils n'auraient pas tous un même biais expérimental...}

@@

We generated 100 uniformly-distributed subsets consisting of 1, 2, 3 and 10 mutants extracted from the Cheng dataset~\cite{Cheng2017}, which we supplemented with the original wild-type sequence (WT).
For each set of probing profiles \bsi{c'est ce qui correspondrait chez nous à du DMS Map mg ilu ce qu'il a fait. Tu peux l'insérer la avec notre nomenclature entre paranthèse step ?}, we executed \OurTool{} with default parameters, using a sample size of 1~000 structures. 
We also analyzed the WT sequence alone, reproducing the analysis 100 times to compare the variability across sets of mutants to the one induced by stochastic aspects of our method. 
Finally, we performed a restricted analysis focusing on the WT, supplemented with 2 probing profiles selected from the 20 most similar conditions to the WT , as assessed by the ensemble distance metrics. By comparing our results with those obtained for unrestricted pairs of mutants, we assess the influence of structure variability on the quality of our predictions. We report in Figure~\ref{fig:variantanalysis} the distribution of MCC values associated with the first prediction returned by \OurTool.

>>>>

% Enter dates of publication
\copyrightyear{??}
\pubdate{???????}
\pubyear{????}
\jvolume{??}
\jissue{??}

@@

\history{%
Received July 1, 2019;
Revised ??????;
Accepted ??????}

@@

\subsection*{The \OurTool{} method}
We introduce the Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles (\OurTool{}), a novel approach that integrates the signal produced by various chemical probes. It performs clustering based on multiple sets of structures sampled in different experimental conditions, to ultimately return a set of structures that are representative of the dominant clusters. Its underlying rationale is that the prominent presence of a stable secondary structure within the  (pseudo-)Boltzmann ensembles induced by multiple experimental conditions should increase its likelihood to be (one of) the native structure(s) for a given RNA. It is thus hoped that integrating several reactivity profiles may be used to promote the native structure as one of the dominant structures within the multi-ensemble, and help circumvent the limitation of pseudo-energies derived from single reactivity profile, which are generally not sufficient to elect the native structure as its minimum (pseudo)-free energy candidate. In other words, combining ensembles of structures generated using multiple probing experiments is likely to denoise the Boltzmann (multi-)ensemble, and thus mitigate systematic biases induced by experimental conditions and reagents.

@@

Our method, summarized in Figure~\ref{fig:approach}, takes as input a set $\mathcal{D}$ of probing experiments, each materialized by a reactivity profile. It starts by producing sets of representatives structures for each of the reactivity profiles using a SHAPE-directed variant of the classic Ding-Lawrence algorithm~\citep{Ding2003}. Following Deigan\etal\cite{Deigan2009}, soft constraints are used to complement the free energy contributions of the classic Turner energy model with pseudo energy contributions resulting from reactivity profiles derived from SHAPE probing experiments.  Given a reactivity $R_i$ for a position $i$, we associate a free-energy bonus to unpaired positions, defined as
$$\Delta G(i) = m \log(R_i +1 )+b$$ 
using $m=1.3$ and  $b=-0.4$. Those values differ from those used by Deigan\etal\cite{Deigan2009}, and were adapted based on the rationale that lower absolute values for pseudo-energy bonuses increase the chance of structures being simultaneously supported by multiple conditions. Those pseudo energy contributions effectively direct our predictions towards a subset of structures that are in good agreement with probing data.

@@

\paragraph{Cheng  \emph{et al} dataset.} 
Starting from the assumption that a functional structure should be preserved during evolution, we wanted to assess the agreement that might exist between probing data profiles for a set of RNA mutants. 
We considered DMS probing data, generated by~\cite{Cheng2017} through systematic point-wise mutations, for the Lariat-capping ribozyme (equivalent to \Cond{DMS}{mg}{MaP}{ilu}{} in the nomenclature below). We renormalized each reactivity profile following the method introduced by Deigan\etal\cite{Deigan2009}, restricted to the primer-free sequence: values greater than $1.5 $ times the interquartile range were discarded, and remaining values were divided by the mean of the top $10\%$ reactivities.  Overall, this constitutes a collection of 188 sequences, each having its associated reactivity profile.

@@

\paragraph{Stops-inducing probing protocol (SHAPE-CE).} 
6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature during 10 minutes in the probing buffer (40 mM HEPES at 7.5 pH, 100 mM KCl, in presence or absence of 5 mM MgCl$_\text{2}$. After a 10 minutes incubation at 37\degree{}C, RNAs were treated with 2 mM of SHAPE reagent or DMSO (negative control) and incubated for 2 (BzCN), 5 (1M7), 30 (NMIA) or 60 (NAI) minutes at 37\degree{}C. Modified or unmodified RNAs were purified by ethanol precipitation and pellets were resuspended in 10 $\mu$l of water.
Modifications were revealed by reverse transcription using 5' fluorescently labelled primers (D2 or D4 WellRED, Sigma Aldrich 5' CTG-TGA-ACT-AAT-GCT-GTC-CTT-TAA 3') and M-MLV RNAse (H-) reverse transcriptase (Promega) as previously described~\cite{Deforges2017}, with only minor modification of the originally described SHAPE protocol~\cite{Wilkinson2006}. cDNAs were separated by capillary electrophoresis (Beckman Coulter, Ceq8000). Data were analyzed using the  \Software{QuSHAPE}~\cite{Karabiber2013} software. RNA probing was performed in triplicate with distinct RNA preparations. The corresponding data sets are named after the probe followed by {\sc CE}, and {\sc mg} if probed in presence of MgCl$_\text{2}$.

@@

For \OneMSevILUThreeMg, the denaturation step was repeated three times : After a 1 minute incubation at 95\degree{}C, 10 mM of 1M7 was added and the mix was incubated 1 minute at 95\degree{}C. This step was repeated 3 times (3D). For 1M7, 1M7Mg, NMIA and NMIAMg, experiments were conducted as described above, except that the NGS library preparation was adapted to Ion Torrent sequencing. Sequences were mapped and analyzed with \Software{ShapeMapper2} for \OneMSevILUThreeMg and \OneMSevILUThreeMg. For the other conditions they are mapped with a script based on \Software{ShapeMapper}, but adapted to Ion Torrent output files. The corresponding data sets are named after the probe followed by {\sc MaP}. The presence of {\sc mg} as a superscript indicates the presence of MgCl$_\text{2}$, while the subscript {\sc il} (Illumina) or {\sc it} (Ion Torrent) specify the sequencing technology.

\paragraph{DiMethylSulfate (DMS) and CMCT probing.}
DMS and CMCT probing were conducted essentially as described in~\cite{Weill2004,James2008}. Succinctly, 6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature for 10 minutes in a probing buffer for DMS probing (40 mM HEPES pH 7.5, 100 mM KCl, 5 mM MgCl$_\text{2}$) or in CMCT (50 mM of potassium borate pH 8, 100 mM KCl and 5 mM MgCl$_\text{2}$). For DMS, RNA was then treated with 1 $\mu$l of DMS (1:12 in ethanol) or 1 $\mu$l of ethanol for 5 minutes at 37\degree{}C (mock reaction), the reaction was stopped by addition of 400 mM of Tris at 7.5 pH and immediately put on ice. For CMCT,  RNA was treated with 10 $\mu$l of CMCT (42 mg/mL) or 10 $\mu$l H$_\text{2}$O for 10 minutes at 37\degree{}C (mock reaction). Modified RNA were ethanol-precipitated and resuspended in 10 $\mu$l of water. Modifications were mapped as described above for SHAPE-CE experiments.The corresponding data sets are named after the probe, followed by {CE} and {\sc mg}.

@@

	\caption{Model of the Lariat capping ribozyme from {\itshape Didymium iridis} (A -- PDB 4P8Z:A by Meyer\etal\cite{Meyer2014}), secondary structure, as annotated by \Software{DSSR} (B -- pseudoknot ommitted) and \OurTool first-ranking prediction (C.), obtained from the integration of 8 maximally-diverging probing conditions (\NMIAMg, \OneMSevILUThreeMg, \NAIMg, \OneMSevCE, \CMCTMg,\OneMSevILUThree, and \OneMSevMgCE).\label{fig:didy}}
\end{figure*}
As benchmark RNA we used the Lariat capping ribozyme from \textit{Didymium Iridis} (DiLCrz) which 3D structure has been modeled at 3.85 \AA{} from X-ray diffraction data~\cite{Meyer2014}. This RNA contains a large diversity of interactions, including helical domains, tertiary pairings, a kissing loop and a pseudoknot (Figure~\ref{fig:didy}).
It was probed as described in Material and Methods in 16 different conditions using different SHAPE and classical reagents, in presence/absence of Mg$^\text{2+}$ ions, using either the standard premature stop or the newly developed mutation induction technologies to map the modification sites. These experimental results were then used as input of \OurTool{}, either individually or combined,  for secondary structure prediction.

@@

The average ensemble distance and PCA visualization support a status of outliers for conditions in the cluster \Bull{B} (\OneMSevCE, \NMIACE, \BzCN, and \NAICE).  We hypothesize that such conditions may be either representative of alternative conformations, or be altogether erroneous. Consequently, we will single out this cluster within our detailed analysis of the multi-probing performances.

%\bsi{sauf erreur de ma part le cluster B des parias c'est tous les CE sans Mg .je me demande s'ils n'auraient pas tous un même biais expérimental...}

@@

We generated 100 uniformly-distributed subsets consisting of 1, 2, 3 and 10 mutants extracted from the Cheng dataset~\cite{Cheng2017}, which we supplemented with the original wild-type sequence (WT).
For each set of probing profiles (\Cond{DMS}{mg}{MaP}{ilu}{}), we executed \OurTool{} with default parameters, using a sample size of 1~000 structures. 
We also analyzed the WT sequence alone, reproducing the analysis 100 times to compare the variability across sets of mutants to the one induced by stochastic aspects of our method. 
Finally, we performed a restricted analysis focusing on the WT, supplemented with 2 probing profiles selected from the 20 most similar conditions to the WT , as assessed by the ensemble distance metrics. By comparing our results with those obtained for unrestricted pairs of mutants, we assess the influence of structure variability on the quality of our predictions. We report in Figure~\ref{fig:variantanalysis} the distribution of MCC values associated with the first prediction returned by \OurTool.

### 2019-06-21 SuppMat.tex
Updates from Overleaf

\section*{Multiprobing benchmark (Cordero~\emph{et al}~\cite{Cordero2012} dataset)}
\subsection*{Structure prediction ordered by RNA}

@@

\section*{Case-study: Lariat capping ribozyme of {\itshape Didymium iridis}}
\subsection*{Compatibility of accessibility profiles with native and predicted structures}
\begin{table}[H]
 \Heatset{min=20,  
	max=60,   
	max colour=BadCol, % colour at maximum
	min colour=Aquamarine3,      % colour at minimum
	Min colour=Aquamarine3, % colour for values below min
	Max colour=BadCol   % colour for values above max
}
 \HeatSecset{min=60,  
	max=85,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{center}
\begin{tabular}{llHHS}
	\toprule
	         &                    &      \multicolumn{2}{c}{Distance of reactivity (\%)}      &                       \\
	Cluster  & Condition          & \multicolumn1c{to prediction} & \multicolumn1c{to native} & \multicolumn1c{MCC\%} \\ \toprule
	\Bull{C} & \OneMSevILUMg      & 23                            & 29                        & 85                    \\
	\Bull{A} & \OneMSevILU        & 32                            & 40                        & 84                    \\
	\Bull{A} & \NMIAMg            & 26                            & 27                        & 81                    \\
	\Bull{A} & \NMIA              & 30                            & 38                        & 80                    \\
	\Bull{C} & \OneMSevILUThreeMg & 42                            & 38                        & 74                    \\
	\Bull{E} & \NMIAMgCE          & 46                            & 39                        & 73                    \\
	\Bull{G} & \NAIMg             & 38                            & 39                        & 73                    \\
	\Bull{H} & \BzCNMg            & 38                            & 29                        & 71                    \\
	\Bull{E} & \OneMSevMgCE       & 48                            & 42                        & 70                    \\
	\Bull{G} & \CMCTMg            & 49                            & 45                        & 70                    \\
	\Bull{D} & \OneMSevILUThree   & 33                            & 39                        & 64                    \\
	\Bull{F} & \DMSMg             & 38                            & 38                        & 63                    \\
	\Bull{B} & \NMIACE            & 31                            & 38                        & 61                    \\
	\Bull{B} & \OneMSevCE         & 38                            & 41                        & 60                    \\
	\Bull{B} & \BzCN              & 51                            & 46                        & 60                    \\
	\Bull{B} & \NAICE             & 41                            & 44                        & 60                    \\ \bottomrule
\end{tabular}
\end {center}
\caption{Distance of the predicted structure from the considered probing data.}
\end{table}

>>>>

\section*{Multiprobing benchmark (Cordero~\emph{et al}~\cite{Cordero2012} dataset)}
\subsection*{MCC values of individual predictions}

@@

\section*{Case-study: Lariat capping ribozyme of {\itshape Didymium iridis}}
\subsection*{Compatibility of accessibility profiles with native and predicted structures}
We assess and validate the overall quality of probing data using a basic notion of distance between discretized profiles and structure. More precisely, given a secondary structure $S$ of length $n$, we define the {\bf 1D projection} of $S$ as the vector $v_S$ such that
$$ \forall i\in[1,n], v_S(i)=\begin{cases} 1 &\text{if $i$ unpaired in $S$}\\ 0 &\text{otherwise.} \end{cases} $$

Given a vector $R$ of reactivities, we define a {\bf discrete reactivity} vector $d_R$ as
$$ \forall i\in[1,n], d_R(i)=\begin{cases} 1 &\text{if $R[i]$ within the $30\%$ largest reactivity values}\\ 
0 & \text{if $R[i]$ within the $30\%$ lowest reactivity values}\\
1/2 &\text{otherwise.} \end{cases} $$
By focusing on the largest and lowest values, we avoid the influence of outliers, and hope to partially mitigate the natural variability of probing reactivities.

We now define the {\bf normalized distance} $||R,S||$ of a reactivity profile $R$ and a structure $S$ as
$$ ||R,S|| = \frac{\sum_{i=1}^n |v_S(i)-d_R(i)|-40\%\times \frac{n}{2}}{n\times 60\%}.$$
Note that exactly 40\% of the positions are assigned to $1/2$, leading to $|v_S(i)-d_R(i)|=1/2$ irrespectively of the value taken by $v_S(i)$. The overall contribution of $40\%\times \frac{n}{2}$ needs to be corrected for, thus the subtraction. The divisor term of $n\times 60\%$ accounts for the fact that, after compensating for the contribution of the $[30,70]$ percentile, only $60\%$ of the original values are effectively covered by the sum. We thus renormalize by $n\times 60\%$ to obtain a final value scaling between $0$ (all highly reactive pos. unpaired, all lowly reactive pos. paired) and $1$ (all highly reactive pos. paired, all lowly reactive pos. unpaired).
\begin{table}[H]
 \Heatset{min=20,  
	max=60,   
	max colour=BadCol, % colour at maximum
	min colour=Aquamarine3,      % colour at minimum
	Min colour=Aquamarine3, % colour for values below min
	Max colour=BadCol   % colour for values above max
}
 \HeatSecset{min=60,  
	max=85,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
{\centering
\begin{tabular}{llHHS}
	\toprule
	         &                    &      \multicolumn{2}{c}{Distance of reactivity (\%)}      &                       \\
	Cluster  & Condition          & \multicolumn1c{to prediction} & \multicolumn1c{to native} & \multicolumn1c{MCC\%} \\ \toprule
	\Bull{C} & \OneMSevILUMg      & 23                            & 29                        & 85                    \\
	\Bull{A} & \OneMSevILU        & 32                            & 40                        & 84                    \\
	\Bull{A} & \NMIAMg            & 26                            & 27                        & 81                    \\
	\Bull{A} & \NMIA              & 30                            & 38                        & 80                    \\
	\Bull{C} & \OneMSevILUThreeMg & 42                            & 38                        & 74                    \\
	\Bull{E} & \NMIAMgCE          & 46                            & 39                        & 73                    \\
	\Bull{G} & \NAIMg             & 38                            & 39                        & 73                    \\
	\Bull{H} & \BzCNMg            & 38                            & 29                        & 71                    \\
	\Bull{E} & \OneMSevMgCE       & 48                            & 42                        & 70                    \\
	\Bull{G} & \CMCTMg            & 49                            & 45                        & 70                    \\
	\Bull{D} & \OneMSevILUThree   & 33                            & 39                        & 64                    \\
	\Bull{F} & \DMSMg             & 38                            & 38                        & 63                    \\
	\Bull{B} & \NMIACE            & 31                            & 38                        & 61                    \\
	\Bull{B} & \OneMSevCE         & 38                            & 41                        & 60                    \\
	\Bull{B} & \BzCN              & 51                            & 46                        & 60                    \\
	\Bull{B} & \NAICE             & 41                            & 44                        & 60                    \\ \bottomrule
\end{tabular}\\}
\caption{Distance of the predicted structure from the considered probing data.}
\end{table}
